Classifying Patents Based on their Semantic Content\thanks{Addresses: Bergeaud: Banque de France (antonin.bergeaud@banque-france.fr), Potiron: Keio University, Raimbault: ISC-PIF }

### 2018-11-10 Docs/Papers/Technical/overleafv2/S4_Text.tex
slides_seminar

\documentclass[12pt,twoside,a4paper]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[section]{placeins}
\usepackage[top=1.5in,bottom=1in,right=1in,left=1in,headheight=15pt]{geometry}
\usepackage{setspace}
\usepackage{rotating}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{etoolbox}
\usepackage{amsmath,amssymb}
\usepackage{float}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{booktabs,caption,fixltx2e}
\usepackage[flushleft]{threeparttable}
\usepackage{tabularx}
\usepackage{booktabs,caption,fixltx2e}
\usepackage[flushleft]{threeparttable}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{caption}
\usepackage{nameref}
\usepackage{lscape}
\usepackage{fancyhdr}

\setcounter{MaxMatrixCols}{10}
\hypersetup{
    colorlinks, linkcolor={dark-red},
    citecolor={blue}, urlcolor={blue}, linkcolor={blue}
}
\geometry{hmargin=4cm,vmargin=4cm}
\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{assumption}{Assumption}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
\setcounter{secnumdepth}{5}
\textwidth 6.0in
\textheight 8.84in 
\setlength{\topmargin}{-0.3in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\abovecaptionskip}{0pt}
\setlength{\belowcaptionskip}{5pt}
\setlength{\textfloatsep}{25pt}  
\setlength{\intextsep}{5pt}   
\fancyhf{}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{1pt}
\fancyhead[LO]{\textit{Classifying Patents Based on their Semantic Content}}
\fancyhead[RE]{\textit{Bergeaud, Potiron, and Raimbault}}
\fancyfoot[C]{\thepage}

\begin{document}

\title{Classifying Patents Based on their Semantic Content\thanks{%
Addresses - Bergeaud: London School of Economics; Potiron: Faculty of Business and Commerce, Keio University, Tokyo, Japan;
Raimbault: UMR CNRS 8504 G{\'e}ographie-cit{\'e}s, Universit{\'e} Paris VII, Paris, France and UMR-T 9403 IFSTTAR LVMT, Ecole Nationale des Ponts et Chauss{\'e}es, Champs-sur-Marne, France.} \vspace{5mm} }
\author{Antonin Bergeaud \ \ \ \ \ Yoann Potiron
 \ \ \ \ \ Juste Raimbault \bigskip}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%
% Please keep the abstract below 300 words
\begin{abstract}
In this paper, we extend some usual techniques of classification resulting from a large-scale data-mining and network approach. This new technology, which in particular is designed to be suitable to big data, is used to construct an open consolidated database from raw data on 4 million patents taken from the US patent office from 1976 onward. To build the pattern network, not only do we look at each patent title, but we also examine their full abstract and extract the relevant keywords accordingly. We refer to this classification as \emph{semantic approach} in contrast with the more common \emph{technological approach} which consists in taking the topology when considering US Patent office technological classes. Moreover, we document that both approaches have highly different topological measures and strong statistical evidence that they feature a different model. This suggests that our method is a useful tool to extract endogenous information.    
\end{abstract}

\pagebreak
%\linenumbers

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Innovation and technological change have been described by many scholars as the main drivers of economic growth as in \cite{aghionhowitt1992} and \cite{romer1990}. \cite{RePEc:nbr:nberwo:3301} advertised the use of patents as an economic indicator and as a good proxy for innovation. Subsequently, the easier availability of comprehensive databases on patent details and the increasing number of studies allowing a more efficient use of these data (e.g.~\cite{Hall2001}) have opened the way to a very wide range of analysis. Most of the statistics derived from the patent databases relied on a few key features: the identity of the inventor, the type and identity of the rights owner, the citations made by the patent to prior art and the technological classes assigned by the patent office post patent's content review. Combining this information is particularly relevant when trying to capture the diffusion of knowledge and the interaction between technological fields as studied in \cite{Youn:2015fk}. With methods such as citation dynamics modeling discussed in~\cite{2013arXiv1310.8220N} or co-authorship networks analysis in~\cite{2014arXiv1402.7268S}, a large body of the literature such as~\cite{sorenson2006complexity} or~\cite{kay2014patent} has studied patents citation network to understand processes driving technological innovation, diffusion and the birth of technological clusters. Finally, \cite{bruck2016recognition} look at the dynamics of citations from different classes to show that the laser/ink-jet printer technology resulted from the recombination of two different existing technologies.

Consequently, technological classification combined with other features of patents can be a valuable tool for researchers interested in studying technologies throughout history and to predict future innovations by looking at past knowledge and interaction across sectors and technologies. But it is also crucial for firms that face an ever changing demand structure and need to anticipate future technological trends and convergence (see, e.g., \cite{curran2011patent}) to adapt to the resulting increase in competition discussed in~\cite{Katz1996remarks} and to maintain market share. Curiously, and in spite of the large number of studies that analyze interactions across technologies~\cite{Furman2011shoulders}, little is known about the underlying ``innovation network'' (e.g. ~\cite{AAKnetwork2016}).

In this monograph, we propose an alternative classification based on semantic network analysis from patent abstracts and explore the new information emerging from it. In contrast with the regular technological classification which results from the choice of the patent reviewer, semantic classification is carried automatically based on the content of the patent abstract. Although patent officers are experts in their fields, the relevance of the existing classification is limited by the fact that it is based on the state of technology at the time the patent was granted and cannot anticipate the birth of new fields.\footnote{To correct for this, the USPTO regularly make changes in its classification in order to adapt to technological change (for example, the ``nanotechnology'' class (977) was established in 2004 and  retroactively to all relevant previously granted patents).} In contrast we don't face this issue with the semantic approach. The semantic links can be clues of one technology taking inspiration from another and  good predictors of future technology convergence (e.g.~\cite{preschitschek2013} study semantic similarities from the whole text of 326 US-patents on \textit{phytosterols} and show that semantic analysis have a good predicting power of future technology convergence). One can for instance consider the case of the word \textit{optic}. Until more recently, this word was often associated with technologies such as photography or eye surgery, while it is now almost exclusively used in a context of semi-transistor design and electro-optic. This semantic shift did not happen by chance but contains information on the fact that modern electronic extensively uses technologies that were initially developed in optic.

Previous research has already proposed to use semantic networks to study technological domains and detect novelty. ~\cite{yoon2004text} was one of the first to enhance this approach with the idea of visualizing keywords network illustrated on a small technological domain. The same approach can be used to help companies identifying the state of the art in their field and avoid patent infringement as in \cite{park2014semantic} and \cite{yoon2011detecting}. More closely related to our methodology,~\cite{gerken2012new} develop a method based on patent semantic analysis of patent to vindicate the view that this approach outperform others in the monitoring of technology and in the identification of novelty innovation. Semantic analysis has already proven its efficiency in various fields, such as in technology studies (e.g.~\cite{choi2014patent} and~\cite{fattori2003text}) and in political science (e.g.~\cite{2015arXiv151003797G}).

Building on such previous research, we make several contributions by fulfilling some shortcomings of existing studies, such as for example the use of frequency-selected single keywords. First of all, we develop and implement a novel fully-automatized methodology to classify patents according to their semantic abstract content, which is to the best of our knowledge the first of its type. This includes the following refinements for which details can be found in Section \ref{keywords}: (i) use of multi-stems as potential keywords; (ii) filtering of keywords based on a second-order (co-occurrences) relevance measure and on an external independent measure (technological dispersion); (iii) multi-objective optimization of semantic network modularity and size. The use of all this techniques in the context of semantic classification is new and essential from a practical perspective.

Furthermore, most of the existing studies rely on a subsample of patent data, whereas we implement it on the full US Patent database from 1976 to 2013. This way, a general structure of technological innovation can be studied. We draw from this application promising qualitative stylized facts, such as a qualitative regime shift around the end of the 1990s, and a significant improvement of citation modularity for the semantic classification when comparing to the technological classification. These thematic conclusions validate our method as a useful tool to extract endogenous information, in a complementary way to the technological classification.

Finally, the statistical model introduced in Section \ref{statisticalmodel} seems to indicate that patents tend to cite more similar patents in the semantic network  when fitted to data. In particular, this propensity is shown to be significantly bigger than the corresponding propensity for technological classes, and this seems to be consistent over time. On the account of this information, we believe that patent officers could benefit very much from looking at the semantic network when considering potential citation candidates of a patent in review.

The paper is organized as follows. Section \ref{data} presents the patent data, the existing classification and provide details about the data collection process. Section \ref{keywords} explains the construction of the semantic classes. Section \ref{result} tests their relevance by providing exploratory results. Finally, section \ref{discussion} discusses potential further developments and conclude. More details, including robustness checking, figures and technical derivations can be found in~\nameref{sectionSI}.

%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background \label{data}}
%%%%%%%%%%%%%%%%%%%%%%%%

In our analysis, we will consider all utility patents granted in the United States Patent and Trademark Office (USPTO) from 1976 to 2013. A clearer definition of utility patent is given in~\nameref{sectionSI}. Also, additional information on how to correctly exploit patent data can be found in \cite{Hall2001} and \cite{lerner2015use}.

%%%%%%%%%%%%%%%%%%%%%
\subsection{An existing classification: the USPC system}

Each USPTO patent is associated with a non-empty set of technological classes and subclasses. There are currently around 440 classes and over 150,000 subclasses constituting the United State Patent Classification (USPC) system. While a technological class corresponds to the technological field covered by the patent, a subclass stands for a specific technology or method used in this invention. A patent can have multiple technological classes, on average in our data a patent has 1.8 different classes and 3.9 pairs of class/subclass. At this stage, two features of this system are worth mentioning: (i) classes and subclasses are not chosen by the inventors of the patent but by the examiner during the granting process based on the content of the patent; (ii) the classification has evolved in time and continues to change in order to adapt to new technologies by creating or editing classes. When a change occurs, the USPTO reviews all the previous patents so as to create a consistent classification.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A bibliographical network between patents: citations \label{sub:citation}}

As with scientific publications, patents must give reference to all the previous patents which correspond to related prior art. They therefore indicate the past knowledge which relates to the patented invention. Yet, contrary to scientific citations, they also have an important legal role as they are used to delimit the scope of the property rights awarded by the patent. One can consult~\cite{oecdpatentmanual} for more details about this. Failing to refer to prior art can lead to the invalidation of the patent (e.g.~\cite{martin2015}). Another crucial difference is that the majority of the citations are actually chosen by the  examiners and not by the inventors themselves. 
From the USPTO, we gather information of all citations made by each patent (backward citations) and all citations received by each patent as of the end of 2013 (forward citations). We can thus build a complete network of citations that we will use later on in the analysis.

Turning to the structure of the lag between the citing and the cited patent in terms of application date, we see that the mean of this lag is 8.5 years and the median is 7 years. This distribution is highly skewed, the $95^{th}$ percentile is 21 years. We also report 164,000 citations with a negative time lag. This is due to the fact that some citations can be added during the examination process and some patents require more time to be granted than others.

In what follows, we choose to restrict attention to pairs of citations with a lag no larger than 5 years. We impose this restriction for two reasons. First, the number of citations received peaks 4-5 years after application. Second, the structure of the citation lag is necessarily biased by the truncation of our sample: the more recent patents mechanically receive less citations than the older ones. As we are restricting to citations received no later than 5 years after the application date, this effect will only affect patents with an application date after 2007.

%%%%%%%%%%%%%%%%%%
\subsection{Data collection and basic description}
Each patent contains an abstract and a core text which describe the invention.\footnote{To see what a patent looks like in practice, one can refer to the USPTO patent full-text database \url{http://patft.uspto.gov/netahtml/PTO/index.html} or to Google patent which publishes USPTO patents in $pdf$ form at \url{https://patents.google.com}.} Although including the full core texts would be natural and probably very useful in a systematic text-mining approach as done in~\cite{tseng2007text}, they are too long to be included and thus we consider only the abstracts for the analysis. Indeed, the semantic analysis counts more than 4 million patents, with corresponding abstracts with an average length of 120.8 words (and a standard deviation of $62.4$), a size that is already challenging in terms of computational burden and data size. In addition, abstracts are aimed at synthesizing purpose and content of patents and must therefore be a relevant object of study (see~\cite{Adams2010text}). The USPTO defines a guidance stating that an abstract should be ``a summary of the disclosure as contained in the description, the claims, and any drawings; the summary shall indicate the technical field to which the invention pertains and shall be drafted in a way which allows the clear understanding of the technical problem, the gist of the solution of that problem through the invention, and the principal use or uses of the invention'' (PCT Rule 8).

We construct from raw data a unified database. Data is collected from USPTO patent redbook bulk downloads, that provides as raw data (specific \texttt{dat} or \texttt{xml} formats) full patent information, starting from 1976. Detailed procedure of data collection, parsing and consolidation are available in~\nameref{sectionSI}. The latest dump of the database in \texttt{Mongodb} format is available at %\url{http://37.187.242.99/files/public/USPTOredbook.gz}.
\url{http://dx.doi.org/10.7910/DVN/BW3ACK} % keep the dataverse hidden for now
Collection and homogenization of the database into a directly usable database with basic information and abstracts was an important task as USPTO raw data formats are involved and change frequently.

We count 4,666,365 utility patents with an abstract granted from 1976 to 2013.\footnote{A very small number of patents have a missing abstract, these are patents that have been withdrawn and we do not consider them in the analysis.} The number of patents granted each year increases from around 70,000 in 1976 to about 278,000 in 2013. When distributed by the year of application, the picture is slightly different. The number of patents steadily increase from 1976 to 2000 and remains constant around 200,000 per year from 2000 to 2007. Restricting our sample to patent with application date ranging from 1976 to 2007, we are left with 3,949,615 patents. These patents cite 38,756,292 other patents with the empirical lag distribution that has been extensively analyzed in~\cite{Hall2001}. Conditioned on being cited at least once, a patent receives on average 13.5 citations within a five-year window. 270,877 patents receive no citation during the next five years following application, 10\% of patents receive only one citation and 1\% of them receive more than 100 citations. A within class citation is defined as a citation between two patents sharing at least one common technological class. Following this definition, 84\% of the citations are within class citations. 14\% of the citations are between two patents that share the exact same set of technological classes.

%%%%%%%%%%%%%%%%%%%%%
\subsection{Towards a Complementary Classification}

Potentialities of text-mining techniques as an alternative way to analyze and classify patents are documented in~\cite{tseng2007text}. The author's main argument, in support of an automatic classification tool for patent, is to reduce the considerable amount of human effort needed to classify all the applications. The work conducted in the field of natural language processing and/or text analysis has been developed in order to improve search performance in patent databases, build technology map or investigate the potential infringement risks prior to developing a new technology (see~\cite{abbas2014literature} for a review). Text-mining of patent documents is also widely used as a tool to build networks which carry additional information to the simplistic bibliographic connections model as argued in~\cite{yoon2004text}. As far as the authors know, the use of text-mining as a way to build a global classification of patents remains however largely unexplored. One notable exception can be found in~\cite{preschitschek2013} where semantic-based classification is shown to outperform the standard classification in predicting the convergence of technologies even in small samples. Semantic analysis reveals itself to be more flexible and more quickly adaptable to the apparition of new clusters of technologies. Indeed, as argued in~\cite{preschitschek2013}, before two distinct technologies start to clearly converge, one should expect similar words to be used in patents from both technologies.

Finally, a semantic classification where patents are gathered based on the fact that they share similar significant keywords has the advantage of including a network feature that cannot be found in the USPC case, namely that each patent is associated with a vector of probability to belong to each of the semantic classes (more details on this feature can be found in Section \ref{characteristics}). Using co-occurrence of keywords, it is then possible to construct a network of patents and to study the influence of some key topological features.

%%%%%%%%%%%%%%%%%%%%%
\section{Semantic Classification Construction \label{keywords}}

In this section, we describe methods and empirical analysis leading to the construction of semantic network and the corresponding classification.

%%%%%%%%%%%%%%%%%%%%%
\subsection{Keywords extraction}
\label{keywordsextraction}

Let $\mathcal{P}$ be the set of patents, we first assign to a patent $p\in \mathcal{P}$ a set of potentially significant keywords $K(p)$ from its text ${\mathcal{A}}(p)$ (that corresponds to the concatenation of its own title and abstract).
$K(p)$ are extracted through a similar procedure as the one detailed in~\cite{chavalarias2013phylomemetic}: 
\begin{enumerate}
\item Text parsing and Tokenization: we transform raw texts into a set of words and sentences, reading it (parsing) and splitting it into elementary entities (words organized in sentences).

\item Part-of-speech tagging: attribution of a grammatical function to each of the tokens defined previously.

\item Stem extraction: families of words are generally derived from a unique root called stem (for example \texttt{compute}, \texttt{computer}, \texttt{computation} all yield the same stem \texttt{comput}) that we extract from tokens. At this point the abstract text is reduced to a set of stems and their grammatical functions.
\item Multi-stems construction: these are the basic semantic units used in further analysis. They are constructed as groups of successive stems in a sentence which satisfies a simple grammatical function rule. The length of the group is between 1 and 3 and its elements are either nouns, attributive verbs or adjectives. We choose to extract the semantics from such nominal groups in view of the technical nature of texts, which is not likely to contain subtle nuances in combinations of verbs and nominal groups.
\end{enumerate}

Text processing operations are implemented in \texttt{python} in order to use built-in functions \texttt{nltk} library~\cite{nltk} for most of above operations. This library supports most of state-of-the-art natural language processing operations.\footnote{Source code is openly available on the repository of the project: \url{https://github.com/JusteRaimbault/PatentsMining} 
}

%%%%%%%%%%%%%%%%%%%%
\subsection{Keywords relevance estimation}
\label{keywords_est}
\paragraph*{Relevance definition}

Following the heuristic in~\cite{chavalarias2013phylomemetic}, we estimate relevance score in order to filter multi-stem. The choice of the total number of keywords to be extracted $K_w$ is important, too small a value would yield similar network structures but including less information whereas very large values tend to include too many irrelevant keywords. We choose to set this parameter to $K_w = 100,000$. We first consider the filtration of $k\cdot K_w$ (with $k=4$) to keep a large set of potential keywords but still have a reasonable number of co-occurrences to be computed. This is done on the \emph{unithood} $u_i$, defined for keyword $i$ as $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the multi-stem's number of apparitions over the whole corpus and $l_i$ its length in words. A second filtration of $K_w$ keywords is done on the \emph{termhood} $t_i$. The latter is computed as a chi-squared score on the distribution of the stem's co-occurrences and then compared to a uniform distribution within the whole corpus. Intuitively, uniformly distributed terms will be identified as plain language and they are thus not relevant for the classification. More precisely, we compute the co-occurrence matrix $(M_{ij})$, where $M_{ij}$ is defined as the number of patents where stems $i$ and $j$ appear together. The \emph{termhood} score $t_i$ is defined as

\[
t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}.
\]

\paragraph*{Moving window estimation}
The previous scores are estimated on a moving window with fixed time length following the idea that the present relevance is given by the most recent context and thus that the influence vanishes when going further into the past. Consequently, the co-occurrence matrix is chosen to be constructed at year $t$ restricting to patent which applied during the time window $\big[ t - T_0 ; t \big]$. Note that the causal property of the window is crucial as the future cannot play any role in the current state of keywords and patents. This way, we will obtain semantic classes which are exploitable on a $T_0$ time span. For example, this enables us to compute the modularity of classes in the citation network as in section \ref{citationmodularity}. In the following, we take $T_0 = 4$ (which corresponds to a five year window) consistently with the choice of maximum time lag for citations made in Section \ref{sub:citation}. Accordingly, the sensitivity analysis for $T_0=2$ can be found in Appendix~\nameref{app:sensitivity}.

%%%%%%%%%%%%%%%%%%%%
\subsection{Construction of the semantic network}
\label{construction}

We keep the set of most relevant keywords $\mathcal{K}_W$ and obtain their co-occurrence matrix as defined in Section \ref{keywords_est}. This matrix can be directly interpreted as the weighted adjacency matrix of the semantic network. At this stage, the topology of raw networks does not allow the extraction of clear communities. This is partly due to the presence of hubs that correspond to frequent terms common to many fields (e.g. \texttt{method}, \texttt{apparat}) which are wrongly filtered as relevant. We therefore introduce an additional measure to correct the network topology: the concentration of keywords across technological classes, defined as:

$$c_{tech}(s) = \displaystyle \sum_{j=1}^{N^{(tec)}} \frac{k_j(s)^2}{ \left(\sum_i k_i(s)\right)^2},$$

where $k_j(s)$ is the number of occurrences of the $s$th keyword in each of the $j$th technological class taken from one of the $N^{(tec)}$ USPC classes. The higher $c_{tech}$, the more specific to a technological class the node is. For example, the terms \texttt{semiconductor} is widely used in electronics and does not contain any significant information in this field. We use a threshold parameter and keep nodes with $c_{tech}(s) > \theta_c$. In a similar manner, edge with low weights correspond to rare co-occurrences and are considered as noise: we filter edges with weight lower than a threshold $\theta_w$, following the rationale that two keywords are not linked ``by chance'' if they appear simultaneously a minimal number of time. To control for size effect, we normalize by taking $\theta_w = \theta_w^{(0)}\cdot N_P$ where $N_P$ is the number of patents in the corpus ($N_P = \left|\mathcal{P} \right|$). Communities are then extracted using a standard modularity maximization procedure as described in~\cite{clauset2004finding} to which we add the two constraints captured by $\theta_w$ and $\theta_c$, namely that edges must have a weight greater than $\theta_w$ and nodes a concentration greater than $\theta_c$. At this stage, both parameters $\theta_c$ and $\theta_w^{(0)}$ are unconstrained and their choice is not straightforward. Indeed, many optimization objectives are possible, such as the modularity, network size or number of communities. We find that modularity is maximized at a roughly stable value of $\theta_w$ across different $\theta_c$ for each year, corresponding to a stable $\theta_w^{(0)}$ across years, which leads us to choose $\theta_w^{(0)} = 4.1\cdot 10^{-5}$. Then for the choice of $\theta_c$, different candidates points lie on a Pareto front for the bi-objective optimization on number of communities and network size, among which we take $\theta_c = 0.06$ (see Fig.~\ref{fig:networksensitivity}).

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
%\hspace{-2.5cm}
\includegraphics[width=0.45\textwidth,height=0.25\textheight]{comnum_thetaw_2004.jpg}
\includegraphics[width=0.45\textwidth,height=0.25\textheight]{comnum_vcount_pareto_2004.jpg}
%\includegraphics[width=\textwidth]{tiff/Fig1.tif}
\caption{\textbf{Sensitivity analysis of network community structure to filtering parameters.} We consider a specific window 2000-2004 and the obtained plots are typical. \textit{(Left panel)} We plot the number of communities as a function of $\theta_w$ for different $\theta_c$ values. The maximum is roughly stable across $\theta_c$ (dashed red line). \textit{(Right panel)} To choose $\theta_c$, we do a Pareto optimization on communities and network size: the compromise point (red overline) on the Pareto front (purple overline: possible choices after having fixed $\theta_w^{(0)}$; blue level gives modularity) corresponds to $\theta_c = 0.06$.}
\label{fig:networksensitivity}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\textwidth]{striking.jpg}
%\includegraphics[width=\textwidth]{tiff/Fig2.tif}
\caption{\textbf{An example of semantic network visualization.} We show the network obtained for the window 2000-2004, with parameters $\theta_c = 0.06$ and $\theta_w = \theta_w^{(0)}\cdot N_P = 4.5e^{-5} \cdot 9.1e^{5}$. The corresponding file in a vector format (\texttt{.svg}), that can be zoomed and explored, is available at \texttt{http://37.187.242.99/files/public/network.svg}.}
\label{fig:rawnetwork}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

\subsection{Characteristics of Semantic Classes}
\label{characteristics}
For each year $t$, we define as $N^{(sem)}_t$ the number of semantic classes which have been computed by clustering keywords from patents appeared during the period $\big[ t-T_0, t \big]$ (we recall that we have chosen $T_0=4$). Each semantic class $k =  1, \cdots, N^{(sem)}_t$ is characterized by a set of keywords $K(k,t)$ which is a subset of $\mathcal{K}_W$ selected as described in Section \ref{keywordsextraction} to Section \ref{construction}. The cardinal of $K(k, t)$ distribution across each semantic class $k$ is highly skewed with a few semantic classes containing over $1,000$ keywords, most of them with roughly the same number of keywords. In contrast, there are also many semantic classes with only two keywords. There are around 30 keywords by semantic class on average and the median is 2 for any $t$. Fig.~\ref{fig:mean_K} shows that the average number of keywords is relatively stable from 1976 to 1992 and then picks around 1996 prior to going down.

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{meancomsize.jpg}
%\includegraphics[width=\textwidth]{tiff/Fig3.tif}
\caption{\textbf{This figure plots the average number of keywords by semantic class for each time window $\left[t-4; t\right]$} from $t=1980$ to $t=2007$.}
\label{fig:mean_K}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

\paragraph*{Title of semantic classes}
USPC technological classes are defined by a title and a highly accurate definition which help retrieve patents easily. The title can be a single word (e.g.: class 101: ``Printing'') or more complex (e.g.: class 218: ``High-voltage switches with arc preventing or extinguishing devices''). As our goal is to release a comprehensive database in which each patent is associated with a set of semantic classes, it is necessary to give an insight on what these classes represent by associating a short description or a title as in~\cite{tseng2007text}. In our case, such description is taken as a subset of keywords taken from $K(k,t)$. For the vast majority of semantic classes that have less than 5 keywords, we decide to keep all of theses keywords as a description. For the remaining classes which feature around 50 keywords on average, we rely on the topological properties of the semantic network.~\cite{yang2000improving} suggest to retain only the most frequently used terms in $K(k,t)$. Another possibility is to select 5 keywords based on their network centrality with the idea that very central keywords are the best candidates to describe the overall idea captured by a community. For example, the largest semantic class in 2003-2007 is characterized by the keywords: \texttt{Support Packet; Tree Network; Network Wide; Voic Stream; Code Symbol Reader}.

\paragraph*{Size of technological and semantic classes} 
We consider a specific window of observations (for example 2000-2004), and we define $Z$ the number of patents which appeared during that time window. For each patent $i=1, \cdots, Z$ we associate a vector of probability where each component $p_{ij}^{(sem)} \in \big[ 0,1 \big]$, with  $j = 1, \cdots, N{(sem)}$ and where\footnote{When there is no room for confusion, we drop the subscript $t$ in $N_t^{(sem)}$.} 
$$\displaystyle \sum_{j=1}^{N^{(sem)}} p_{ij}^{(sem)} = 1.$$ On average across all time windows, a patent is associated to 1.8 semantic classes with a positive probability. Next we define the size of a semantic class as $$S_j^{(sem)} = \displaystyle \sum_{i=1}^Z p_{ij}^{(sem)}.$$ 
Correspondingly, we aim to provide a consistent definition for technological classes. For that purpose, we follow the so-called ``fractional count'' method, which was introduced by the USPTO and consists in dividing equally the patents between all the classes they belong to. Formally, we define the number of technological classes as
$N^{(tec)}$  (which is not time dependent contrary to the semantic case) and for $j = 1, \cdots, N^{(tec)}$ the corresponding matrix of probability is defined as
\[
 p_{ij}^{(tec)} = \frac{B_{ij}}{\displaystyle \sum_{k=1}^{N^{(tec)}}{B_{ik}}},
\]
where  $B_{ij}$ equals $1$ if the $i$th patent belongs to the $j$th technological class and $0$ if not. When there is no room for confusion, we will drop the exponent part and write only $p_{ij}$ when referring to either the technological or semantic matrix. Empirically, we find that both classes exhibit a similar hierarchical structure in the sense of a power-law type of distribution of class sizes as shown in Fig.~\ref{fig:class-sizes}. This feature is important, it suggests that a classification based on the text content of patents has some separating power in the sense that it does not divide up all the patents in one or two communities.

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\hspace*{-2.5cm}
\includegraphics[width=1.2\textwidth]{all_raw_counts.jpg}
%\includegraphics[width=\textwidth]{tiff/Fig4.tif}
\caption{\textbf{Sizes of classes.} Yearly from $t = 1980$ to $t =2007$, we plot the size of semantic classes (left-side) and technological classes (right-side) for the corresponding time window $[t-4, t]$, 
from the biggest to the smallest. The formal definition of size can be found in Section \ref{characteristics}. Each color corresponds to one specific year. Yearly semantic classes and technological classes present a similar hierarchical structure which confirms the comparability of the two classifications. This feature is crucial for the statistical analysis in Section \ref{statisticalmodel}. Over time, curves are translated and levels of hierarchy stays roughly constant.}
\label{fig:class-sizes}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\subsection{Potential Refinements of the Method}

Our semantic classification method could be refined by combining it with other techniques such as Latent Dirichlet Allocation which is a widely used topic detection method (e.g.~\cite{blei2003latent}), already used on patent data as in~\cite{kaplan2015double} where it provides a measure of idea novelty and the counter-intuitive stylized facts that breakthrough invention are likely to come out of local search in a field rather than distant technological recombination. Using this approach should first help further evaluate the robustness of our qualitative conclusions (external validation). Also, depending on the level of orthogonality with our classification, it can potentially bring an additional feature to characterize patents, in the spirit of multi-modeling techniques where neighbor models are combined to take advantage of each point of view on a system.

Our use of network analysis can also be extended using newly developed techniques of hyper-network analysis. Indeed, patents and keywords can for example be nodes of a bipartite network, or patents be links of an hyper-network, in the sense of multiple layers with different classification links and citation links. \cite{iacovacci2015mesoscopic} provide a method to compare macroscopic structures of the different layers in a multilayer network that could be applied as a refinement of the overlap, modularity and statistical modeling studied in this paper. Furthermore, is has recently been shown that measures of multilayer network projections   induce a significant loss of information compared to the generalized corresponding measure~\cite{de2015ranking}, which confirms the relevance of such development that we left for further research.

%%%%%%%%%%%%%%%%%%%%%%
\section{Results \label{result}}
%%%%%%%%%%%%%%%%%%%%%

In this section, we present some key features of our resulting semantic classification showing both complementary and differences with the technological classification. We first present several measures derived from this semantic classification at the patent level: Diversity, Originality, Generality (Section \ref{subsec:orig-gene}) and Overlapping (Section \ref{subsec:overlaps}). We then show that the two classifications show highly
different topological measures and strong statistical evidence that they feature a different model (Sections \ref{citationmodularity} and \ref{statisticalmodel}).

%%%%%%%%%%%%%%%%%%%%%%

\subsection{Patent Level Measures}  \label{subsec:orig-gene}

Given a classification system (technological or semantic classes), and the associated probabilities $p_{ij}$ for each patent $i$ to belong to class $j$ (that were defined in Section \ref{characteristics}), one can define a patent-level diversity measure as one minus the Herfindhal concentration index on $p_{ij}$  by

\[
D_i^{(z)} = 1 - \sum_{j =1}^{N^{(z)}} {p_{ij}^2}, \text{ with } z \in \{tec, sem\}.
\]

We show in Fig.~\ref{fig:patent-level-orig} the distribution over time of semantic and technological diversity with the corresponding mean time-series. This is carried with two different settings, namely including/not including patents with zero diversity (i.e. single class patents). We call other patents ``complicated patents'' in the following. First of all, the presence of mass in small probabilities for semantic but not technological diversity confirms that the semantic classification contains patent spread over a larger number of classes. More interestingly, a general decrease of diversity for complicated patents, both for semantic and technological classification systems, can be interpreted as an increase in invention specialization. This is a well-known stylized fact as documented in~\cite{ARCHIBUGI199279}. Furthermore, a qualitative regime shift on semantic classification occurs around 1996. This can be seen whether or not we include patents with zero diversity. The diversity of complicated patents stabilizes after a constant decrease, and the overall diversity begins to strongly decrease. This means that on the one hand the number of single class patents begins to increase and on the other hand complicated patents do not change in diversity. It can be interpreted as a change in the regime of specialization, the new regime being caused by more single-class patents.

>>>>

\input{si.tex}
